Explain urban regional function

### 2018-11-22 paper.tex
1122

\keywords{Explanation  \and Urban computing \and Online content \and Sentiment analysis \and Latent Factor \and Post hoc.}
\end{abstract}
%

\section{Introduction}
%urban computing
Urban computing is a process of acquisition, integration and analysis of big and heterogeneous data generated by diverse sources in urban spaces~\cite{Zheng2014UrbanConcepts}. 
Recently, urban computing has attracted attentions from both academy and industry.
One critical step towards efficient urban computing is to identify functional regions, which is a region in a city that supports certain needs of urban lives~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}.

%related work survey
Most of previous functional region identification systems use clustering methods on mobility data~\cite{Karlsson2006FunctionalRegionSummary}. such as origin-destination pairs of labour market data~\cite{Karlsson2006FunctionalRegionSummary}.
For example, clustering algorithm based on the 'modularity function' is applied on telecommunication data~\cite{Newman2004ModularityFunction,Ratti2010Telecom}, semantic labeling framework based on the Latent Dirichlet Allocation is applied on remote-sensor data~\cite{Vatsavai2010Remote}, spectural clustering is applied on remote-sensor image data~\cite{Vatsavai2011Remote}, and DMR (Dirichlet Multinomial Regression) are applied on pick-ups and drop-offs data of taxicabs and points of interests (POIs)~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}.

%problem of past research
A severe drawback of existing research is the lack of explanation for functional regions.
Clustering methods have long been suffering from the subjective issue, i.e. the system only provides one possible partitioning of the regions while the users have no idea what the partitioning means. 
Furthermore, to obtain accurate identification, recent research tends to use complex models~\cite{Yuan2015FunctionRegion} on a combination of different data sources. 
The complex nature of these models is an obstacle for people to capture the ``semantics'' of the identification.

%motivation
Explainable functional region identification is beneficial for both system designers and end users.
For example, providing explanations help system designers to better intepretate the clustering results and improve the system. 
The explanations can incubate a series of applications for end users, including traffic flow predictions, personalized trajectory recommendation, urban planning and so on. 
In a bigger picture, there is a growing interest in studying explainable AI~\cite{Preece2018ExplainAI}.
However, in geographical systems, explainable system is still in its initial stage~\cite{Korpan2017navigation,Jose2018cognitive}.

%goal
In this paper, we present a novel system for explainable functional region identification. The system provides post-hoc explanations, i.e. the explanations are not relevant to the identification algorithm. Instead, the system attempts to resolve the ``semantics" of cluster labels generated by any functional region identification algorithm by (1) associating the cluster labels to a set of human activities; (2) visualizing the desired urban features and public sentiments for each activity; and (3) listing the most important urban features in the region.

As shown in Fig.\ref{explanation-example}, the city of Chengdu has been functional regions delivers explanations of the  functionals. To be specific, we first associate each functional with an urban activity, next we extract the most representative urban feature for each activity, finally we highlight the sentiment towards typical urban features for each functional region.  For example,Fig.\ref{explanation-example} given a map of city A, reg region I corresponds to residential region while blue region II corresponds to commercial region. We found that people are most interested on traffic for a commercial region. And a residential region usually has sentiment positive on vanishing noise.

%explain implementation, we need to incorporate activity and online sentiment
\textbf{Framework.}
In this paper,to make the results more convincing, we build a system that provides explanations for functional region clustering results.
The system is built upon two data sets. One is mobility data including more than 3 million pick-up and drop-off coordinates and timestamps,which provide fuzzy flow increment of each region units and each time bins.
The increment, also called moving patterns, are the first input of topic-model-based DMR models as well as POIs.
Dirichlet Multinomial Regression(DMR) identify the segmented region units as different functions.
Meanwhile, comment data of shop show the sentiment relavitity between urban feature and the activity that shop related to.
We pick labels with highest information entropy as urban features from all extracted features.
Finally, we optimal latent factor with temporal dimension to get a location-feature matrix.

@@

\textbf{Challenge.}
In order to solve the problem, we face two challenges.

The first one of it is to extract the urban feature from comment data.
Urban feature is a set of characters with special geographical attributes, e.g., clothes, school, bars and so on.
Most of our content data are comments of shops with the shop address.The feature extracted from it is more related to shop feature than urban feature.
Therefore, existing sentiment extraction model ~\cite{Lu2011Label} can not be used directly in our models.%urban feature
In order to get the location information from these content data, all features are extracted as~\cite{Zhang2015Sentires}.
We select typical features with a high frequency and high information entropy from it.

And the second challenge is how to explain the features.
If the extracted urban features used for explanations can not correspond to the labeled activity used to identify functional regions, the explanations will not have a strong explanation power for the identification, or even will not be generated.
To improve the explanation power of our framework, we extract related urban feature and find the corresponding sentiment score between activity and urban feature from contents.
With the probability that region units belong to which function generated by DMR, we can applied matrix factorization to find the relativity between region units and latent factor, i,e urban feature.
The urban feature with highest relativity make an explanation for why corresponding region units are identified as such function.

@@

\textbf{Structure.}
The remainder of the paper is organized as follows.
We give an overview for related work in Section 2.
In Section 3, we give an overview of our framework.
Section 4 shows the process of functional region identification as well as urban feature extraction.
And Section 5 introduces the post hoc explanation model.
We test the framework on our datasets and presents the superior explanation result in Section 6
Finally, we made a conclusion and looked forward to our future work in Section 7.

>>>>

\keywords{Explainable AI  \and Urban computing \and Online Sentiment analysis \and Big data analysis \and Functional region identification}
\end{abstract}
%

\section{Introduction}
%urban computing
Urban computing is a process to acquire, integrate and analyze big and heterogeneous data generated by diverse sources in urban spaces~\cite{Zheng2014UrbanConcepts}. 
Recently, urban computing has attracted attentions from both academy and industry.
One critical step towards efficient urban computing is to identify \emph{functional regions}, which are regions in a city that support certain needs of urban lives~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}.

%related work survey
Most of previous \emph{Functional Region Identification} (FRI) systems use clustering methods on mobility data~\cite{Karlsson2006FunctionalRegionSummary}.
For example, clustering algorithm based on the 'modularity function' is applied on telecommunication data~\cite{Newman2004ModularityFunction,Ratti2010Telecom}, spectral clustering is applied on remote-sensor image data~\cite{Vatsavai2011Remote}, variants of Latent Dirichlet Allocation (LDA) is applied on remote-sensor data~\cite{Vatsavai2010Remote} and taxicab pick-ups and drop-offs data~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}.

%problem of past research
A severe drawback of existing research is the lack of explanation for functional regions.
Clustering methods generate cluster labels that have long been suffering from the subjective issue, i.e. the system only provides one possible partitioning of the regions while the users have no idea what the partitioning means. 
Furthermore, to obtain accurate identification, recent research tends to use complex models such as the Dirichlet Multinomial Regression model in~\cite{Yuan2015FunctionRegion} . 
The complex nature of these models is an obstacle for people to capture the ``semantics'' of the clustering results.

%motivation
There is a strong incentive to develop explainable FRI system, which \emph{explains} the identification of functional regions. 
Explainable FRI is beneficial for both system designers and end users.
For system designers, providing explanations help them better diagnose the system and improve system performance. 
For end users, explanations not only facilitate interpretation of the clustering results, but also incubate a wide range of applications, including traffic flow predictions, personalized trajectory recommendation, urban planning and so on.

%goal
Though there is a growing interest in studying explainable AI~\cite{Preece2018ExplainAI}, in geographical systems, explainable system is still in its initial stage~\cite{Korpan2017navigation,Jose2018cognitive}.
In this paper, we present a novel system for explainable FRI by integrating heterogeneous data sources. Our system provides post-hoc explanations, i.e. the explanations are not relevant to the FRI algorithm. Instead, for an arbitrary FRI algorithm, the system attempts to resolve the ``semantics" of the generated cluster labels by (1) associating the cluster labels to a set of human activities; (2) visualizing the desired urban features for each activity; and (3) listing the most important urban features in the region.

%figure ??? real example or made-up example
As shown in Fig.\ref{explanation-example}, the city has been partitioned into several functional regions. For a specific region $r_1$ with label $I$, the system delivers textual and visual descriptions. Firstly label $l$ is most likely to relate to a mixture of activities ``'' and ``'', because from the analysis of mobility data, these two activities bring in $\%$ of the traffic flow to region $r_1$. Secondly, under activity ``", two urban features ``'' and ``" are most popular, with highly positive sentiments collected from online reviews. Finally region $r_1$'s most representative urban features are exactly ``" and ``", thus the system \textbf{explains} why $r_1$ is labeled as $l$.

%highlight
We highlight a key property of the proposed system: the power to integrate heterogenous data sources. On one hand, explanations essentially involve semantics. In our system, the semantics of labels are expressed through urban activities and urban features, which are extracted from online review data. On the other hand, the cluster labels are obtained in mobility data. To obtain more reasonable explanations that comply with the clustering algorithm, the semantics are blended with moving patterns discovered in mobility data. In building such a system, we face two challenges.

@@

%manual label costly supervision in sufficient
The first one of it is to extract the urban feature from comment data.
Urban feature is a set of characters with special geographical attributes, e.g., clothes, school, bars and so on.
Most of our content data are comments of shops with the shop address.The feature extracted from it is more related to shop feature than urban feature.
Therefore, existing sentiment extraction model ~\cite{Lu2011Label} can not be used directly in our models.%urban feature
In order to get the location information from these content data, all features are extracted as~\cite{Zhang2015Sentires}.
We select typical features with a high frequency and high information entropy from it.

%unsupervised

%how to embed mobility data
And the second challenge is how to explain the features.
If the extracted urban features used for explanations can not correspond to the labeled activity used to identify functional regions, the explanations will not have a strong explanation power for the identification, or even will not be generated.
To improve the explanation power of our framework, we extract related urban feature and find the corresponding sentiment score between activity and urban feature from contents.
With the probability that region units belong to which function generated by DMR, we can applied matrix factorization to find the relativity between region units and latent factor, i,e urban feature.
The urban feature with highest relativity make an explanation for why corresponding region units are identified as such function.

%bias curve

@@

The remainder of the paper is organized as follows.
We give an overview for related work in Section 2.
In Section 3, we give an overview of our framework.
Section 4 shows the process of functional region identification as well as urban feature extraction.
And Section 5 introduces the post hoc explanation model.
We test the framework on our datasets and presents the superior explanation result in Section 6
Finally, we made a conclusion and looked forward to our future work in Section 7.
